### 2019-07-12 manuscript/results.tex
fixed up pathways figure
added a diagram of the two pathways
nicer fonts and spacing in the plots
discussion notes-to-self
- fixed %Boris mark in introduction - added modified pathstates fig to separate and match line type
Adding the correct figures and tables to results and first part of supplement

@@

\begin{supptable}
    \begin{center}

    \begin{tabular}{lcccccc}
                       & D/P   & D/P+A/B      & I/C    & I/C+A/B      & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %                                                                                      
        $r_D$          & 0.260 & 0.193, 0.658 & ---    & ---          & ---      & ---          \\
        $r_P$          &-0.056 & 0.030, 0.187 & ---    & ---          & ---      & ---          \\
        $r_I$          & ---   & ---          & 0.550  & 0.386, 0.877 & ---      & ---          \\
        $r_C$          & ---   & ---          &-0.001  &-0.059, 0.606 & ---      & ---          \\
        $r_{ID}$       & ---   & ---          & ---    & ---          & 0.455    & 0.309, 0.797 \\
        $r_{CD}$       & ---   & ---          & ---    & ---          & 0.065    &-0.006, 0.587 \\
        $r_{CP}$       & ---   & ---          & ---    & ---          &-0.088    &-0.074, 0.403 \\
        %                                                                                      
        $\rho$         & 0.047 & 0.047        & ---    & ---          & ---      & ---          \\
        $\rho_I$       & ---   & ---          & ---    & ---          & 0.067    & 0.053        \\
        $\rho_C$       & ---   & ---          & ---    & ---          & 0.033    & 0.032        \\
        $q_{IC}$       & ---   & ---          & 0.364  & 0.261        & 0.198    & 0.145        
    \end{tabular}

    \vspace{12pt}

    \begin{tabular}{lcccc}
                       & D/P   & D/P+A/B      & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %                                                              
        $r_D$          & 0.382 & 0.698, 0.100 & ---      & ---          \\
        $r_P$          & 0.109 & 0.587, 0.182 & ---      & ---          \\
        $r_I$          & ---   & ---          & ---      & ---          \\
        $r_C$          & ---   & ---          & ---      & ---          \\
        $r_{ID}$       & ---   & ---          & 0.449    & 0.318, 0.789 \\
        $r_{CD}$       & ---   & ---          & 0.050    &-0.248, 0.494 \\
        $r_{CP}$       & ---   & ---          &-0.027    & 0.110, 0.634 \\
        %                                                              
        $\rho$         & 0.033 & 0.026        & ---      & ---          \\
        $\rho_I$       & ---   & ---          & 0.063    & 0.047        \\
        $\rho_C$       & ---   & ---          & 0.024    & 0.011        \\
        $\delta$       & 0.050 & 0.162        & 0.022    & 0.107        \\
        $q_{IC}$       & ---   & ---          & 0.194    & 0.164        
    \end{tabular}

    \end{center}
    \caption{
        Median rate estimates for all fitted models.
        Units are per million years.
        Two comma-separated numbers refer to the $A$ and $B$ hidden states, and --- means the parameter was not present in the model.
    Net diversification rates ($r$) are subscripted with trait state initials (Diploid, Polyploid, Incompatible, Compatible). Transition rates are $\rho$ (polyploidization), subscripted with background breeding system state; $\delta$ (diploidization); and  $q_{IC}$ (loss of self-incompatibility).
    The upper section is for models without diploidization, and the lower section is for models with diploidization.
    The supplemental figures show the corresponding distributions of parameter estimates.
    }
    \label{table:estimates}
\end{supptable}

@@

%B: heads up: I added two clarifying descriptive sentences in the two figures below. Maybe something about noting x-axis scale differences would be useful.
\begin{figure}
\includegraphics[width=\textwidth]{allnetdivmodelswithoutdelta.pdf} % FIXME: need horizontal axis label
\caption{Net diversification rates for all models without diploidization rate estimate. 
Each panel contains a graphical summary of estimated model parameters and displays posterior distributions for net diversification estimates.}
\label{figure:netdivall}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{allnetdivmodelsdiploidization.pdf}
\caption{Net diversification rates for all models that include diploidization ($\delta$). 
Each panel contains a graphical summary of estimated model parameters and displays posterior distributions for net diversification estimates.}  
\label{figure:netdivnodip}
\end{figure}

% E todo: include a diagram of the transitions (panels a/b at the top?); re-run with new rate estimates; add panel letters
\begin{figure}
    \centering \includegraphics[width=0.9\textwidth]{pathways}
    \caption{
        Contributions of the two pathways to polyploidy.
        The one-step pathway is direct ID$\rightarrow$CP transitions.
        The two-step pathway consists of ID$\rightarrow$CD$\rightarrow$CP transitions.
        When considering only rates of transitions among the states (ignoring the diversification rate parameters), the one-step pathway dominates on short timescales and the two-step on long timescales (left panels).
        When also considering diversification within each state, the one-step pathway, in which polyploidization breaks down SI, dominates over any timescale (right panels).
        The top panels show the separate contributions of each pathway.
        The bottom panels show the proportional contribution of the one-step pathway (\ie one-step / [one-step + two-step]).
    }
    \label{figure:pathways}
\end{figure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrDP.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node of the D/P ploidy model} % XXX
\label{suppfigure:DPnodipasr}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrDPdelta.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the D/P+ $\delta$, ploidy model} % XXX
\label{suppfigure:DPasr}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrDPAB.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the D/P D/P+A/B ploidy model} % XXX
\label{suppfigure:DPnodipABasr}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrDPABdelta.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the D/P+$\delta$+A/B ploidy model.} % XXX
\label{suppfigure:DPABasr}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrIC.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the I/C breeding system model} % XXX
\label{suppfigure:ICasr}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrICAB.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the I/C+A/B breeding system model} % XXX
\label{suppfigure:ICABasr}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrIDCDCP.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP ploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodipasr}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrIDCDCPdelta.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP+$\delta$ ploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPasr}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrIDCDCPAB.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP+A/B polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodipABasr}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{asrIDCDCPdeltaAB.pdf}
\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP+$\delta$+A/B, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPABasr}
\end{suppfigure}

>>>>

% see Will's notes in discussion.tex, FIXME
%   also use transition rates from transition-only (no diversification) analysis
%   also use stochatic maps, (a) for CP tips, what paths were taken? (b) for steps away from ID, which path was started?

@@

\begin{supptable}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                           & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M7    & M8     & M9    & M10   & Evidence                                                                                     \\ \hline
M6. D/P+$\delta$                & -1268.83                                                          & 55.41 & 42.78  & 53.37 & 52.85 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M6\end{tabular}            \\ \hline
\textbf{M7. CID D/P+$\delta$}   & \textbf{-1212.42}                                                 &       & -12.62 & -2.04 & -2.04 & \begin{tabular}[c]{@{}l@{}}Model M7 moderately\\ preferred over M9 and M10\end{tabular}      \\ \hline
M8. D/P+A/B $\delta$            & -1214.46                                                          &       &        & 10.58 & 10.07 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular} \\ \hline
M9. D/P+A/B +$\delta$ asym      & -1214.46                                                          &       &        &       & -0.51 & No evidence                                                                                  \\ \hline
M10. D/P+A/B +$\delta$ all asym & -1214.97                                                          &       &        &       &       &         \\ \hline                                                                                    
\end{tabular}
\caption{Bayes factors of  ploidy only models with diplodization. Results indicate that a character independent model (M6) is strongly preferred over BiSSE (M1)  model. M6 is moderately preferred over any of the HiSSE model swith asymmetric hidden rates (M9, M10).}
\label{supptable:M6M10}
\end{supptable}

\begin{supptable}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                            & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M18   & M19   & M20   & Evidence                                                                                                   \\ \hline
M16. ID/CP/CD                    & -1459.11                                                          & 45.11 & 65.91 & 63.98 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M16\end{tabular}                         \\ \hline
M17. CID ID/CP/CD                & *                                                                 &       &       &       &                                                                                                            \\
M18. ID/CP/CD+A/B                & -1414                                                             &       & 20.79 & 18.87 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}               \\ \hline
\textbf{M19. ID/CP/CD +A/B asym} & \textbf{-1393.20}                                                 &       &       & -1.92 & \begin{tabular}[c]{@{}l@{}}Asymmetric hidden rates moderately\\ preferred over all asymmetric\end{tabular} \\ \hline
M20. ID/CP/CD +A/B all asym      & -1393.12                                                          &       &       &       &   \\ \hline                                                                                                        
\end{tabular}
\caption{Bayes factors of ploidy and breeding system withou diploidization. Results indicate that the MuHiSSE model with asymmetric hidden rates (17) is  strongly preferred over M16 and M18 and moderately preferred over the MuHiSSe with all rates asymetric (M20). *Marginal log-likelihood for M17 could not be calculated in our limited amount of computational time.}
\label{supptable:M16M20}
\end{supptable}

\begin{supptable}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                                 & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M22   & M23    & M24   & M25   & Evidence                                                                                         \\ \hline
M21. ID/CP/CD+$\delta$                & -1454.68                                                          & 55.48 & 46.031 & 67.94 & 65.15 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M21\end{tabular}               \\ \hline
M22. CID ID/CP/CD+$\delta$            & -1399.201                                                         &       & -9.452 & 12.45 & 9.675 & \begin{tabular}[c]{@{}l@{}}Model M24 strongly preferred \\ over M22\end{tabular}                 \\ \hline
M23. ID/CP/CD+A/B $\delta$            & -1408.65                                                          &       &        & 21.91 & 19.12 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}     \\ \hline
\textbf{M24. ID/CP/CD +$\delta$ asym} & \textbf{-1386.74}                                                 &       &        &       & -2.78 & \begin{tabular}[c]{@{}l@{}}Asymmetric hidden rates \\ preferred over all asymmetric\end{tabular} \\ \hline
M25. ID/CP/CD +$\delta$ all asym      & -1389.52                                                          &       &        &       &       &                      \\ \hline                                                                           
\end{tabular}
\caption{Bayes factors of ploidy and breeding system with diploidization. Results indicate that the MuHiSSE model with asymmetric hidden rates (M24) is  strongly preferred over M21-M23 and moderately preferred over the MuHiSSe with all rates asymetric (M25).}
\label{supptable:M21M25}
\end{supptable}

\begin{supptable}
\addtolength{\tabcolsep}{-5pt}
\begin{tabular}{|l|c|c|c|l|}
\hline
Model                                    & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=log(BF(M1,M2) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M3. D/P+A/B                                 & -1234.52                     &    M3 vs. M4                 & 11.239                  & M4 (Strong)   \\
\textbf{M4. D/P+ A/B asym}            & -1223.28                     &   M4 vs. M5              & -1.658                  & M4 (Moderate)   \\
M5. D/P+A/B all asym                 & -1224.93                     &                     &                         &                         \\ \hline
M13. I/C+ A/B                                & -1270.47                     &   M13 vs. M14                  & 22.75                   & M14 (Strong)   \\
\textbf{M14. I/C+ A/B asym}            & \textbf{-1247.72}            & M14 vs. M15         & {0.05}           & No evidence             \\
M15. I/C+ A/B all asym               & -1247.67                     &                     &                         &                         \\ \hline
M18. IC/CD/CP+A/B                            & -1414.00                     &     M18 vs. M19                & 20.79                   & M19 (Strong)    \\
\textbf{M19. IC/CD/CP+ A/B asym}       & \textbf{-1393.21}            & M19 vs. M20          & {-1.919}         & M19 (Moderate)   \\
M20. IC/CD/CP+ A/B all asym           & -1395.129                    &                     &                         &                         \\ \hline
M8. D/P +A/B+$\delta$                          & -1225.05                     &  M8 vs. M9                   & 10.58                   & M9 (Strong)    \\
\textbf{M9. D/P+ A/B+ $\delta$ asym}      & \textbf{-1214.46}                     &    M9 vs. M10                 & -0.52                   & M10 (Moderate) \\
M10. D/P+A/B+$\delta$ all asym        & -1214.98                     &                    &                         &                         \\ \hline
M23. IC/CD/DP+A/B+$\delta$                 & -1408.65                     &     M23 vs M24                & 21.91                   & M24(Strong)     \\
\textbf{M24. IC/CD/DP+A/B+$\delta$ asym} & \textbf{-1386.74}                     &   M24 vs M25              & -2.78                   & M24 (Moderate) \\
M25. IC/CD/DP+A/B+ $\delta$ all asym     & -1389.52                     &                     &                         &                         \\ \hline
\end{tabular}
\caption{Test for symmetry of the hidden and trait rates via Bayes factors. For all models asymmetric hidden transition rates are preferred over models with equal hidden rates. Adding more complexity by assuming asymmetry in the trait rate within hidden states does not improve models.}
\label{supptable:asymmetry}
\end{supptable}

@@

%B: heads up: I added two clarifying descriptive sentences in the two figures below. Maybe something about noting x-axis scale differences would be useful.
\begin{figure}
\includegraphics[width=\textwidth]{alldiversificationasymhidden.pdf} 
\caption{Net diversification rates for all models without diploidization rate estimate. 
Each panel contains a graphical summary of estimated model parameters and displays posterior distributions for net diversification estimates.}
\label{figure:netdivall}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{lumped.pdf} %lumped.pdf
\caption{Comparing two and three state models is possible via lumpable models (M26, M28). These models used the same classifications as the three-state model M16 which allow for comparisons via Bayes Factors as shown in \cref{table:lumped}.}  
\label{figure:lumped}
\end{figure}

% E todo: re-run with new rate estimates; add panel letters?
\begin{figure}
    \centering 
    \includegraphics[width=0.5\textwidth]{pathstates2} \\ [40pt] 
        \includegraphics[width=0.9\textwidth]{pathways}
    \caption{
        Contributions of the two pathways to polyploidy.
        The one-step pathway is direct ID$\rightarrow$CP transitions.
        The two-step pathway consists of ID$\rightarrow$CD$\rightarrow$CP transitions.
        When considering only rates of transitions among the states (ignoring the diversification rate parameters), the one-step pathway dominates on short timescales and the two-step on long timescales (left panels).
        When also considering diversification within each state, the one-step pathway, in which polyploidization breaks down SI, dominates over any timescale (right panels).
        The top panels show the separate contributions of each pathway.
        The bottom panels show the proportional contribution of the one-step pathway (\ie one-step / [one-step + two-step]).
    }
    \label{figure:pathways}
\end{figure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{alldiversificationasymhiddendip.pdf}
\caption{Posterior distribution for all the best models with diploidization} % XXX
\label{suppfigure:alldip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{comparablesDP.pdf}
\caption{Lumped ploidy models to assess the effect of adding breeding system to create a three-state model. Moderate evidence exists that adding a breeding system is necessary \cref{table:lumped} } % XXX
\label{suppfigure:lumpedDP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{comparablesIC.pdf}
\caption{Lumped breeding system models to assess the effect of adding ploidy to create a three-state model. Moderate to insignificant evidence exists that adding ploidy is necessary \cref{table:lumped} } % XXX
\label{suppfigure:lumpedIC}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{effectofasymmetry.pdf}
\caption{Effect of asymmetric rates in hidden models. Models with asymmetric rates are preferred over models with equal rates \cref{supptable:asymmetry}} % XXX
\label{suppfigure:asymmetric}
\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrDP.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node of the D/P ploidy model} % XXX
%\label{suppfigure:DPnodipasr}
%\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrDPdelta.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the D/P+ $\delta$, ploidy model} % XXX
%\label{suppfigure:DPasr}
%\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrDPAB.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the D/P D/P+A/B ploidy model} % XXX
%\label{suppfigure:DPnodipABasr}
%\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrDPABdelta.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the D/P+$\delta$+A/B ploidy model.} % XXX
%\label{suppfigure:DPABasr}
%\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIC.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the I/C breeding system model} % XXX
%\label{suppfigure:ICasr}
%\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrICAB.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the I/C+A/B breeding system model} % XXX
%\label{suppfigure:ICABasr}
%\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIDCDCP.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP ploidy and breeding system model} % XXX
%\label{suppfigure:IDCDCPnodipasr}
%\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIDCDCPdelta.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP+$\delta$ ploidy and breeding system model} % XXX
%\label{suppfigure:IDCDCPasr}
%\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIDCDCPAB.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP+A/B polyploidy and breeding system model} % XXX
%\label{suppfigure:IDCDCPnodipABasr}
%\end{suppfigure}

@@

%\begin{suppfigure}
%\includegraphics[width=\textwidth]{asrIDCDCPdeltaAB.pdf}
%\caption{Ancestral state reconstruction showing the maximum a posteriori for each node in the ID/CD/CP+$\delta$+A/B, polyploidy and breeding system model} % XXX
%\label{suppfigure:IDCDCPABasr}
%\end{suppfigure}

### 2019-07-12 manuscript/tables.tex
Adding the correct figures and tables to results and first part of supplement

@@

\begin{table}[]
\addtolength{\tabcolsep}{-5pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                       & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=log(BF(M1,M2) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M26. Lumped D/P             & -1463.22                                                          & M26 vs. M16 & 4.10            & M16 (Moderate)                                                       \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M27. Lumped D/P+A/B         & -1417.67                                                          & M27 vs. M23 & 3.678           & M23 (Moderate)                                                       \\
\textbf{M23. ID/CD/CP +A/B} & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
M28. Lumped I/C             & -1458.41                                                          & M28 vs. M16 & -0.69           & No evidence                                                          \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M29. Lumped I/C+ A/B        & -1416.60                                                          & M29 vs. M23 & 2.60            & M23 (Moderate)                                                       \\
\textbf{M23. IC/CD/CP+A/B}  & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Test for adding a focal trait to a binary state model via Bayes factors. Three-state modes are moderately preferred over two-state models. The evidence is stronger towards the inclusion of breeding system in ploidy models (M26, M27) than the inclusion of ploidy in breeding system models (M29, M29)}
\label{table:testextrastate}
\end{table}

>>>>

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M2    & M3     & M4    & M5     & Evidence                                                                                     \\ \hline
M1. D/P              & -1283.76                                                          & 59.90 & 49.23  & 60.48 & 58.82  & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M1\end{tabular}            \\ \hline
\textbf{M2. CID D/P} & \textbf{-1223.86}                                                 &       & -10.66 & 0.579 & -1.079 & \begin{tabular}[c]{@{}l@{}}Strong preference for \\ M2 over M1\end{tabular}              \\ \hline
M3. D/P+A/B          & -1234.52                                                          &       &        & 11.24 & 9.58   & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M4. D/P+A/B asym}     & \textbf{-1223.28}                                                          &       &        &       & -1.658 & \begin{tabular}[c]{@{}l@{}}Moderate evidence for\\ only asymmetric hidden rates\end{tabular} \\\hline
M5. D/P+A/B all asym & -1224.93                                                          &       &        &       &        &          \\ \hline                                                                                   
\end{tabular}
\caption{Bayes factors of  ploidy only models without diplodization. Results indicate that a character independent model (M2) is strongly preferred over BiSSE (M1)  model. There is no evidence that character independent model is different from M4, the HiSSE model with asymmetric hidden rates. M4 is moderately preferred over the more complicated M5, a HiSSE model that has asymmetry for all transition rates.}
\label{table:M1M5}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                           & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M7    & M8     & M9    & M10   & Evidence                                                                                     \\ \hline
M6. D/P+$\delta$                & -1268.83                                                          & 55.41 & 42.78  & 53.37 & 52.85 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M6\end{tabular}            \\ \hline
\textbf{M7. CID D/P+$\delta$}   & \textbf{-1212.42}                                                 &       & -12.62 & -2.04 & -2.04 & \begin{tabular}[c]{@{}l@{}}Model M7 moderately\\ preferred over M9 and M10\end{tabular}      \\ \hline
M8. D/P+A/B $\delta$            & -1214.46                                                          &       &        & 10.58 & 10.07 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular} \\ \hline
M9. D/P+A/B +$\delta$ asym      & -1214.46                                                          &       &        &       & -0.51 & No evidence                                                                                  \\ \hline
M10. D/P+A/B +$\delta$ all asym & -1214.97                                                          &       &        &       &       &         \\ \hline                                                                                    
\end{tabular}
\caption{Bayes factors of  ploidy only models with diplodization. Results indicate that a character independent model (M6) is strongly preferred over BiSSE (M1)  model. M6 is moderately preferred over any of the HiSSE model swith asymmetric hidden rates (M9, M10).}
\label{table:M6M10}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                      & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M12   & M13   & M14   & M15   & Evidence                                                                                       \\ \hline
M11. I/C                   & -1309.07                                                          & 41.13 & 38.59 & 61.34 & 61.40 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M111\end{tabular}            \\ \hline
M12. CID I/C               & -1267.93                                                          &       & -2.53 & 20.21 & 20.37 & \begin{tabular}[c]{@{}l@{}}Models with asymmetric rates\\ are preferred over  M12\end{tabular} \\ \hline
M13. I/C+A/B               & -1270.47                                                          &       &       & 22.75 & 22.80 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M14. I/C+A/B asym} & \textbf{-1247.72}                                                 &       &       &       & 0.05 & No evidence                                                                                    \\ \hline
\textbf{M15. I/C+A/B all asym }     & \textbf{ -1247.66}                                                          &       &       &       &       &       \\ \hline                                                                                        
\end{tabular}
\caption{Bayes factors of breeding system only models. Results indicate that the HiSSE models with asymmetric rates (M14, M15) are strongly preferred over every other model.}
\label{table:M11M15}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                            & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M18   & M19   & M20   & Evidence                                                                                                   \\ \hline
M16. ID/CP/CD                    & -1459.11                                                          & 45.11 & 65.91 & 63.98 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M16\end{tabular}                         \\ \hline
M17. CID ID/CP/CD                & *                                                                 &       &       &       &                                                                                                            \\
M18. ID/CP/CD+A/B                & -1414                                                             &       & 20.79 & 18.87 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}               \\ \hline
\textbf{M19. ID/CP/CD +A/B asym} & \textbf{-1393.20}                                                 &       &       & -1.92 & \begin{tabular}[c]{@{}l@{}}Asymmetric hidden rates moderately\\ preferred over all asymmetric\end{tabular} \\ \hline
M20. ID/CP/CD +A/B all asym      & -1393.12                                                          &       &       &       &   \\ \hline                                                                                                        
\end{tabular}
\caption{Bayes factors of ploidy and breeding system withou diploidization. Results indicate that the MuHiSSE model with asymmetric hidden rates (17) is  strongly preferred over M16 and M18 and moderately preferred over the MuHiSSe with all rates asymetric (M20). *Marginal log-likelihood for M17 could not be calculated in our limited amount of computational time.}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                                 & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M22   & M23    & M24   & M25   & Evidence                                                                                         \\ \hline
M21. ID/CP/CD+$\delta$                & -1454.68                                                          & 55.48 & 46.031 & 67.94 & 65.15 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M21\end{tabular}               \\ \hline
M22. CID ID/CP/CD+$\delta$            & -1399.201                                                         &       & -9.452 & 12.45 & 9.675 & \begin{tabular}[c]{@{}l@{}}Model M24 strongly preferred \\ over M22\end{tabular}                 \\ \hline
M23. ID/CP/CD+A/B $\delta$            & -1408.65                                                          &       &        & 21.91 & 19.12 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}     \\ \hline
\textbf{M24. ID/CP/CD +$\delta$ asym} & \textbf{-1386.74}                                                 &       &        &       & -2.78 & \begin{tabular}[c]{@{}l@{}}Asymmetric hidden rates \\ preferred over all asymmetric\end{tabular} \\ \hline
M25. ID/CP/CD +$\delta$ all asym      & -1389.52                                                          &       &        &       &       &                      \\ \hline                                                                           
\end{tabular}
\caption{Bayes factors of ploidy and breeding system with diploidization. Results indicate that the MuHiSSE model with asymmetric hidden rates (M24) is  strongly preferred over M21-M23 and moderately preferred over the MuHiSSe with all rates asymetric (M25).}
\label{table:M21M25}
\end{table}

@@

\begin{table}[]
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                       & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=ln(BF(M1,M2) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M26. Lumped D/P             & -1463.22                                                          & M26 vs. M16 & 4.10            & M16 (Moderate)                                                       \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M27. Lumped D/P+A/B         & -1417.67                                                          & M27 vs. M23 & 3.678           & M23 (Moderate)                                                       \\
\textbf{M23. ID/CD/CP +A/B} & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
M28. Lumped I/C             & -1458.41                                                          & M28 vs. M16 & -0.69           & No evidence                                                          \\
\textbf{M16. ID/CD/CP}      & \textbf{-1459.11}                                                 &             &                 &                                                                      \\ \hline
M29. Lumped I/C+ A/B        & -1416.60                                                          & M29 vs. M23 & 2.60            & M23 (Moderate)                                                       \\
\textbf{M23. IC/CD/CP+A/B}  & \textbf{-1414.00}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Test for adding a focal trait to a binary state model via Bayes factors. Three-state modes are moderately preferred over two-state models. The evidence is stronger towards the inclusion of breeding system in ploidy models (M26, M27) than the inclusion of ploidy in breeding system models (M29, M29)}
\label{table:testextrastate}
\end{table}
